Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-05-31 manuscript.tex
section 3 updates

\xavier{Exoplanets only produce a pure RV signal. Stellar activity on the contrary, and in particular the presence of active regions on the stellar photosphere, does not produce a blueshift or redshift of the entire stellar spectra, but creates a spurious RV signal by modifying the shape of spectral lines. To track these variations in the shape of the spectral lines}, the general approach consists in using the FWHM, the BIS SPAN or the indicators introduced in \citet{Boisse-2011} or \citet{Figueira-2013}, which provide information on the width and asymmetry of the CCF. A strong correlation between the estimated RVs and one or more of these parameters provides an indication that stellar activity signals are affecting our measurements.

>>>>

Exoplanets only produce a pure RV signal. On the contrary, stellar activity, in particular the presence of active regions on the stellar photosphere, do not produce blueshifts or redshifts of the entire stellar spectrum but can create spurious RV signals by modifying the shape of spectral lines.
To track these variations in the shape of the spectral lines, the general approach consists in using the FWHM, the BIS SPAN or other indicators such as those introduced in \citet{Boisse-2011} or \citet{Figueira-2013}, which provide information on the width and asymmetry of the CCF. A strong correlation between the estimated RVs and one or more of these parameters provides an indication that stellar activity signals may be affecting the measurements.
